Scoring_questionnaires2021

### 2021-08-24 Questionnaires_scoring2021.Rmd
345_356 self reports

db_demog<- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))%>%
  subset(!is.na(`Participant Private ID`))

@@

merge 
```{r}

db_self_rep
library(readr)
db_self_rep_350_1 <- read_csv("db_self_rep_350.1.csv")
# View(db_self_rep_350_1)

@@

write_csv(db_self_rep, "db_self_rep_345_356_final.csv")
```

>>>>

# note this is ignoring the last
db_demog <- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))%>%

db_demog <- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))%>%
  subset(!is.na(`Participant Private ID`))

@@

```{r}
# STAI_T:: 5nzr

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_T_5nzr")

# STAIS: 8rfo

library(readxl)
db_STAI_S <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_S_8rfo/data_exp_11458-v9_questionnaire-8rfo_345_356.xlsx")

library(readxl)
db_STAI_T <- read_excel("data_exp_11458-v9_questionnaire-5nzr_345_356.xlsx")

db_STAI_T

# eliminate empty rows
db_STAI_T<- subset(db_STAI_T, db_STAI_T$`Event Index`== 1)

db_STAI_T$completion_code<- db_STAI_T$`Participant Completion Code`

colnames(db_STAI_T)
db_STAI_T1<- db_STAI_T %>%
    select("Participant Private ID","completion_code", 
           STAI_01:STAI_20)%>%
  # drop anything with quantised or text
  select(-contains("quantised"))

# score

colnames(db_STAI_T1)
# do the actual scoring, only on the BPQ part - bpdy awareness
db_STAI_T2<- db_STAI_T1%>%
   mutate(STAIT = rowSums(.[ 3:22]))

db_STAI_T2
db_STAI_T3<- select(db_STAI_T2, c(1:2, 23))
db_STAI_T3

db_STAI_S

# eliminate empty rows
db_STAI_S <- subset(db_STAI_S, db_STAI_S$`Event Index`== 1)

db_STAI_S$completion_code<- db_STAI_S$`Participant Completion Code`

colnames(db_STAI_S)
db_STAI_S1<- db_STAI_S %>%
    select("Participant Private ID","completion_code", 
           STAIS_01:STAIS_20)%>%
  # drop anything with quantised or text
  select(-contains("quantised"))

# score

colnames(db_STAI_S1)
# do the actual scoring, only on the BPQ part - bpdy awareness
db_STAI_S2<- db_STAI_S1%>%
   mutate(STAIS = rowSums(.[ 3:22]))

db_STAI_S2
db_STAI_S3<- select(db_STAI_S2, c(1:2, 23))
db_STAI_S3

db_STAI<- left_join(db_STAI_S3, db_STAI_T3)

merge 
```{r}
db_self_rep
library(readr)
db_self_rep_350_1 <- read_csv("db_self_rep_350.1.csv")
# View(db_self_rep_350_1)

@@

# library(readxl)
Interoception_Study_Logbook <- read_excel("Interoception Study Logbook.xlsx")
View(Interoception_Study_Logbook)

db_self_rep_345_356$completion_code
Interoception_Study_Logbook$completion_code
ssid<- select(Interoception_Study_Logbook, c(1:3))

db_self_rep_345_356<- left_join(db_self_rep_345_356,ssid, by = "completion_code")
write_csv(db_self_rep_345_356, "db_self_rep_345_356_final.csv")

# - CHECK WASI M on the norms

db_age2<- subset(db_age1, !is.na(`Participant Private ID`))
db_age2

db_self_rep_345_356<- left_join(db_self_rep_345_356,db_age2)

db_self_rep_345_356

colnames(db_self_rep_345_356)

db_self_rep_345_356

db_self_rep_345_356<- left_join(db_self_rep_345_356, db_STAI)
